Writing Trash Bin

### 2024-04-17 writingdumpster.qmd
Handful of cuts made when working out what figures to put in each section

# Removed Sections
## Defining Uncertainty
The absence of an encompassing definition of uncertainty is mentioned by every uncertainty visualisation directly [@Spiegelhalter2017; @Griethe2006] or indirectly by describing a myriad of ways it can be considered in the literature [@Kinkeldey2014; @Hullman2016], although it is never commented on as a source of the noise in the field.

@@

>>>>

# Removed Sections
@Munzner2009 created a nested model for visualisation that highlighted how the first mistake that can be made in a visualisation is in the problem characterisation, and failing to do it well can cause downstream effects and damage the effectiveness of a visualisation.

The absence of an encompassing definition of uncertainty is mentioned by every uncertainty visualisation directly [@Spiegelhalter2017; @Griethe2006] or indirectly by describing a myriad of ways it can be considered in the literature [@Kinkeldey2014; @Hullman2016], although it is never commented on as a source of the noise in the field.

@@

Utilizing bias and variance to define uncertainty is well-established, but it is absent concerns about imputed data, assumptions, sampling methods, and even the human element of analyst decisions
